Verifying Demonstrations

### 2017-09-27 SystemModel.tex
Updates definition of participation proof

\begin{definition}[Participation proof]
  A \emph{participation proof} is a tuple \((id; t_s, t_e; lp; \sigma)\), where
  \(id, t_s, t_e\) are as in \cref{DefProtest},
  \(lp\) is a location proof and
  \(\sigma\) is a signature over the proof.
\end{definition}

\begin{frame}
  \mode<presentation>{%
  \begin{definition}[Participation proof]
    \begin{itemize}
      \item A \emph{participation proof} is a tuple \((id; t_s, t_e; lp; 
          \sigma)\), where
      \item \(id, t_s, t_e\) are as before,
      \item \(lp\) is a location proof and
      \item \(\sigma\) is a signature over the proof.
    \end{itemize}
  \end{definition}

  \pause{}
  }
\begin{question}
  How should this one relate to the \acp{LP} and \ac{tposet}?
\end{question}
\end{frame}

>>>>

\begin{definition}[Participation proof]
  A \emph{witness signature}\footnote{%
    \Iac{LPS}?
  }is a tuple \[(pid; id; t_s, t_e; x, y; \sigma),\] where
  \(pid\) is a protester's identity,
  \(id, t_s, t_e, x, y\) are as in \cref{DefProtest} and
  \(\sigma\) is a signature over the values in the tuple.
  A \emph{participation proof} \[P_{i, j} = \{ (pid; id; t_s, t_e; x, y; \sigma) 
    \mid pid = i, id = j\}\] for a protester \(i\) participating in protest 
  \(j\) is the set of all witness signatures with the same protester and protest 
  identifiers.
\end{definition}

\mode<presentation>{%
  \begin{frame}
    \begin{definition}[Participation proof]
      \begin{itemize}
        \item A \emph{witness signature} is a tuple \((pid; id; t_s, t_e; x, y; 
            \sigma)\), where
        \item \(pid\) is a protester's identity,
        \item \(id, t_s, t_e, x, y\) are as before,
        \item \(\sigma\) is a signature over the values.
        \item A \emph{participation proof} \(P_{i, j} = \{ (pid; id; t_s, t_e; x, 
            y; \sigma) \mid pid = i, id = j\}\).
      \end{itemize}
    \end{definition}
  \end{frame}
}
